Programming Language Survey Paper on Haskell

### 2013-04-22 projects/term_paper/paper.tex
Edits on section 3.

The final selection construct in Haskell is case expressions. Case expressions evaluate expressions based on 
the possible cases of a value. They are similar to the standard use of cases, except they can also pattern 
match the input. Note that this is exactly how pattern matching parameters in function definitions works. In 
fact, pattern matching parameters is simply an easier way to write case expressions, and the two are interchangeable.

The following function demonstrates how to evaluate a specific expression that depends on which pattern 
an argument matches by using the `case' construct. Note that if this function were written using the 
pattern matching technique it would work exactly the same way and the code would be more readable.

@@

Inheritance in Haskell can be achieved through class extension, which involves a class defined as a subclass 
of another class. The subclass then inherits all of the operations in the superclass. A benefit to class 
extension is shorter contexts: a type expression for a function that uses operations from both the subclass 
and the superclass only has to use the context of the subclass. Additionally, methods for subclass 
operations can assume the existence of methods for superclass operations.

The following class definition of Ord inherits all of the operations in Eq, but also includes the comparison 
operators as well as maximum and minimum functions.

>>>>

The final selection construct in Haskell is case expressions. Case expressions evaluate expressions based on 
the values of a parameter. They are similar to case constructs in imperative languages, except they can also pattern 
match the input. Note that this is exactly how pattern matching parameters in function definitions works. In 
fact, pattern matching parameters is simply an easier way to write case expressions, and the two are interchangeable.

The following function demonstrates how to evaluate a specific expression that depends on which pattern 
an argument matches by using the \texttt{case} construct. Note that if this function were written using the 
pattern matching technique it would work exactly the same way.

@@

Inheritance in Haskell can be achieved through class extension, which involves defining a class as a subclass 
of some other class. The subclass then inherits all of the operations in the superclass. A benefit to class 
extension is shorter contexts: a type expression for a function that uses operations from both the subclass 
and the superclass only has to use the context of the subclass. Additionally, methods for subclass 
operations can assume the existence of methods for superclass operations.

The following class definition of the \texttt{Ord} typeclass inherits all of the operations in the \texttt{Eq} typeclass but
also obtains comparison operators as well as the \texttt{maximum} and \texttt{minimum} functions.
